\begin{doublespace}
\begin{tightcenter}
ACKNOWLEDGEMENTS
\mylinespacing%
\end{tightcenter}

First and foremost I would like to thank my supervisor Yannick Meurice for his
support and encouragement throughout my entire graduate research experience.
%
I would also like to thank both James Osborn, and Xiao-Yong Jin for their
incredible patience, guidance, and expertise throughout my time at Argonne
National Laboratory.

I would like to thank the University of Iowa Graduate College for their
financial support during the writing of this thesis, and all of the University
of Iowa Department of Physics \& Astronomy Faculty who served as mentors and
helped me navigate the graduate school process.

Finally, I would like to thank Argonne National Laboratory and the US
Department of Energy for their financial support and hospitality.

This research was supported in part by the Office of Science Graduate Student
Research (SCGSR) program. The SCGSR program is administered by the Oak Ridge
Institute for Science and Education (ORISE) for the DOE. ORISE is managed by
ORAU under contract number DE‐SC0014664.

Additional support was provided by DOE grant DE-SC0010113.



% This research was supported in part by the Department of Energy, Office of Science, Office of High Energy Physics,
% Grant No.~DE-SC0013496 (JG) DE-SC0010113 (YM) and DE-SC0009998 (JUY) and Office of Workforce Development for Teachers
% and Scientists, Office of Science Graduate Student Research (SCGSR) program. The SCGSR program is administered by the
% Oak Ridge Institute for Science and Education (ORISE) for the DOE. ORISE is managed by ORAU under contract number
% DE‐SC0014664 (SF).

% Prior to your first thesis deposit, replace this text with your acknowledgements.  This text should be double spaced
% and each paragraph should be indented.  This text may be altered between first and final deposit.

% Prior to your first thesis deposit, replace this text with your acknowledgements.  This text should be double spaced
% and each paragraph should be indented.  This text may be altered between first and final deposit.
% \mylinespacing
% \begin{tightcenter}
% \myoptpg
% \end{tightcenter}
\end{doublespace}
